---
title: "Data Science HW1"
author: "Akanksha Nalatwad"
output: github_document
---

```{r}
library(tidyverse)
```

## Problem 1

Create a data frame comprised of:

* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”

```{r create_df}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "med", "med", "med", "med", "high", "high", "high"))
  )
```
Take the mean of each variable in my data frame.

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

```{r try_numeric}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
```

## Problem 2

```{r}
data("penguins", package = "palmerpenguins")


```
There are `r nrow(penguins)` rows and `r ncol(penguins)` columns in this dataset. 
The species in this dataset include `r unique (pull(penguins, species))` and the islands include `r unique (pull(penguins, island))`.
The variable names in the dataset 'penguins' are: `r names(penguins)`.
The mean flipper length in this data set is `r mean (pull(penguins, flipper_length_mm), na.rm=TRUE)`.

Scatterplot of Flipper length and Bill Length

```{r}
ggplot(data=penguins, aes(x=bill_length_mm, y=flipper_length_mm, color=species))+geom_point()
  ```


